SpARC: Sparse Redundant Calibration

### 2016-09-22 paper.tex
added noise

>>>>

\section{Visibilities}
The observed visibility $d_{pq}$ measured by the baseline formed by antenna $p$ and $q$ can be described as

\begin{equation}
d_{pq} = g_{p}\conj{g}_{q}y_{pq} + n_{pq},
\end{equation}
where $g_{p}$ and $g_{q}$ are the direction independent gains associated with antenna $p$ and $q$, $y_{pq}$ denotes the true visibility that baseline $pq$ measured
and $n_{pq}$ is the thermal noise component. Conjugation is denoted by $\conj{(*)}$. During an actual observation the true value of $g_p$, $g_q$ and $y_{pq}$ are unknown and are the quantities which have 
to be estimated.

The thermal noise is normally distributed with a mean of zero and a standard deviation that is equal to  
\begin{equation}
\sigma = \frac{\sqrt{2}k_{B}T_{\textrm{sys}}}{A\eta\sqrt{\Delta \nu \tau}}, 
\end{equation}
where $k_B$ is Boltzmann's constant, $T_{\textrm{sys}}$ is equal to the system temperature, $A$ is the effective collecting area of each element in the array, $\eta$ is a dimensionless
efficiency factor, $\Delta \nu$ is the observational bandwidth and $\tau$ is the integration time per visibility. The

and $n_{pq}$ 
zero-mean gaussian noise representing thermal noise.
